Report on the Third Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE3)

### 2015-11-06 WSSSPE3/report/WSSSPE3_review.tex
add Yolanda Gil's talk

\item \textbf{Yolanda Gil, Chris Duffy, Chris Mattmann, Erin Robinson and Karan
Venayagamoorthy: \textit{The Geoscience Paper of the Future Initiative: Training
Scientists in Best Practices of Software Sharing}}

>>>>

\item \textbf{Yolanda Gil, Chris Duffy, Chris Mattmann, Erin Robinson and Karan
Venayagamoorthy: \textit{The Geoscience Paper of the Future Initiative: Training
Scientists in Best Practices of Software Sharing}}
Yolanda Gil presented an approach to overcome some hurdles in scientific
publishing: the disconnect between experimental data, research software, and
publications. A current effort in the Geosciences is the ``Geoscience Paper of
the Future'', which includes four elements. Firstly, it forms a modern paper
including both text, data and pointers to supplementary matertial. Secondly, is
reproducible, including data processing, workflow and visualization tools. As
third element, it is part of open science, which includes being publicly
available under open licenses, and providing meta-data. Last, but not least, it
uses digital scholarship elements like persisent identifiers for software,
data, and authors, and it cites both data and software. OntoSoft is an effort
to help this effort, providing software stewardship for the Geosciences. As
part of this inituative, a special issue of a journal in a geoscience areas is
planned that only includes geoscience papers of the future, with submissions
open until the end of 2015. In addition, training sessions are provided to
geoscientists to learn best practices in software and data sharing, provenance
documentation, and scholarly publication.
